--- 
title: "36100 Data Science for Innovation materials"
author: "Simon Knight"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib,packages.bib]
biblio-style: apalike
link-citations: true
nocite: | 
  @*
github-repo: sjgknight/dsi
description: "This is some of the materials we'll use in the class. These materials were published with the package bookdown::gitbook."
---

# Prerequisites

Placeholder


## What's in here?
## To download and use the code...

<!--chapter:end:index.Rmd-->


# Preamble

Placeholder


## First, we're going to load libraries
## Useful other tools or snippets of code
## Garmin
## Walking data (and covid impacts)
## Your location
## Text mining demo
## Sentiment on text
## Named entity recognition
## Image processing Images
## EDA and Descriptive Statistics
## Other fun examples
### search history

<!--chapter:end:01-demo.Rmd-->

---
output:
  html_document:
    df_print: paged
---

# Simplified (very) template

```{r verysimplified}

htmltools::includeHTML("https://raw.githubusercontent.com/sjgknight/DSI-templates/main/AT2_very_simplified/template_very_simplified.html")

```

<!--chapter:end:02-01-templates.Rmd-->

---
output:
  html_document:
    df_print: paged
---

# Simplified Template

```{r simplified}

htmltools::includeHTML("https://raw.githubusercontent.com/sjgknight/DSI-templates/main/AT2_simplified-master/R/template_simplified.html")
```

<!--chapter:end:02-02-templates.Rmd-->

---
output:
  html_document:
    df_print: paged
---

# FlexDashboard (note - more advanced, and this isn't a proper functioning example) 

```{r flexy}
#htmltools::includeHTML("https://raw.githubusercontent.com/sjgknight/DSI-templates/main/AT2_flex_demo/AT2_Template.html")
#See on Rpubs http://rpubs.com/sjgknight/flex_junk

if(!file.exists("vignettes/flex_junk.html")){
  download.file("https://raw.githubusercontent.com/sjgknight/DSI-templates/main/AT2_flex_demo/AT2_template.html", "vignettes/flex_junk.html")
}

knitr::include_url("vignettes/flex_junk.html")

```

<!--chapter:end:02-03-templates.Rmd-->

---
output:
  html_document:
    df_print: paged
---

# Introduction to the AT2 Templates

For your AT2 assignment we ask you to submit your report as a *knitted* file. You **do not** have to write any `r` code to do this. At simplest, you can create all your analysis (data, visualisations) in other programs, and use `rstudio` and `markdown` to embed these, and format your document.

RStudio has made this a lot simpler recently because there is now an inbuilt visual editor (I'm using it right now and it looks almost exactly like a Word document!). Even if you use this view, you should still get familiar with the basics of `markdown`...for example, these little chunks with a grey background are introduced by using the \\\` key (top left on my keyboard) before and after the code example. To make something **bold, we use** \\\* **before and after the words,** and so on.

We've created some templates to help with this, and they are organised by complexity in the next Chapters.

You can download each of these as Project files, either at the guthub repository <https://github.com/sjgknight/DSI-templates> or via drive <https://tinyurl.com/DSIAT2Template> (they should be in sync).

You can see what they look like in the next chapters.

1.  Simplified (very) Template is an introductory one

2.  Simplified Template (suggest using this one if you're happy to play around a bit more, but it's still pretty easy to learn)

3.  FlexDashboard (note - more advanced, and this isn't a proper functioning example) (more advanced...so much so, I couldn't get a functional example working well, so you'd have to be ok fixing it up. You can also embed these in other documents, like this).

<!--chapter:end:02-templates.Rmd-->

---
output:
  html_document:
    df_print: paged
---

# learnr activities

## Setting up

We're going to embed some learnr activities now.  The first one is "live" on the shinyapps.io server.  It will walk you through setting up and running the other later tasks. 

To do this, You're going to download RStudio (if you haven't already), along with the source for this book. 

```{r basics}

#htmltools::includeHTML("hhttps://learnr-examples.shinyapps.io/ex-setup-r/")
knitr::include_url("hhttps://learnr-examples.shinyapps.io/ex-setup-r/")

knitr::include_app("hhttps://learnr-examples.shinyapps.io/ex-setup-r/")

```
## Downloading the resources

```{r getbook}


```


## MatchR

This one...

```{r learnr_matchr, eval=FALSE, include=FALSE}
#You should have this directory locally, and so the first line will work.  If you want to check you have the most current version, uncomment the github lines and run that. 

if (interactive()) {
  rmarkdown::run("matchr/snippet_matchR_clustered.Rmd")
  }

## Only run this example in interactive R sessions
# if (interactive()) {
#   shiny::runGitHub(repo = "dsi", 
#           username = "sjgknight",
#           ref = "main",
#           subdir = "matchr/")
#   }

```

## CleanR

This one...

```{r learnr-clearnr}

```


```{r deploy, eval=FALSE, include=FALSE}
rsconnect::listBundleFiles("matchR/")
rsconnect::deployApp(appFiles = c("matchR/snippet_matchR_clustered.Rmd","matchR/snippet_matchR_clustered.html"), appName = "matchR", appTitle = "matchR")

rsconnect::deployApp(appDir = "matchR/")

#Within a file we use:
runtime: shinyrmd 
```


<!--chapter:end:03-learnr.Rmd-->

---
title: "Template_nav"
output:
  html_document:
    includes:
      after_body:  <iframe src="https://raw.githubusercontent.com/sjgknight/DSI-templates/main/AT2_very_simplified/template_very_simplified.html" title="Embed of very simplified template maybe"></iframe>
---

# Embed of very simplified template maybe

<!--chapter:end:03-template-vsimp.Rmd-->

---
output: bookdown::html_document2
---

In the template file, this line (wrapped in \`\`) is used to insert the references. Testing to see if just using the heading works, with a hash before the reference. r if (knitr::is_html_output()) ' References {-}'

# References

::: {#refs}
:::

<!--chapter:end:06-references.Rmd-->


# Data cleaning in R and OpenRefine

Placeholder


## Setting up in OpenRefine
## Setting up in R
## In OpenRefine
## And in R
## In OpenRefine
## And in R
## In OpenRefine
## And NAs in R

<!--chapter:end:cleaning.Rmd-->

---
title: "Template_nav"
author: "sjgknight"
date: "01/08/2021"
output: html_document
---

You have three options for your AT2 template:
* Very simplified template (first) just embeds images. You'll use a bit of markdown to format things, but all or most of your analysis will be in another program (excel + something to make nicer visualisations perhaps).
* Simplified template (second) which shows how you can include more of your analysis, and make more use of markdown features
* Flexdashboard version - this one is more complex...in fact, the demo doesn't function properly. You can explore flexdashboards, and think about how you could setup the report with panels. OR you could embed a flexdashboard as a component in one of the above files.

```{r, child=c( 'Materials/Templates/AT2_very_simplified/template_very_simplified.Rmd','Materials/Templates/AT2_simplified-master/R/template_simplified.Rmd','Materials/Templates/AT2_flex_demo/AT2_template.Rmd')}

```


<!--chapter:end:Template_nav.Rmd-->

