--- 
title: "36100 Data Science for Innovation materials"
author: "Simon Knight"
date: "`r Sys.Date()`"
#site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib,packages.bib]
biblio-style: apalike
link-citations: true
nocite: | 
  @*
github-repo: sjgknight/dsi
description: "This is some of the materials we'll use in the class. These materials were published with the package bookdown::gitbook."
---

# Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
#install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
library(bookdown)
options(bookdown.render.file_scope = FALSE)
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

## What's in here?
There are: Some vignettes (next), two sample AT2 templates, there is also a third but embedding it currently breaks things. And then references.
There are learnr packages I'll include at some point. 


## For my reference
```{r serve}
#To preview book use the below
#bookdown:::serve_book()
```

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
#This passes a list of all packages loaded in the current session to write_bib, which writes the citations to "packages.bib" Notice we've separated "book.bib" from "packages.bib", so this works for packages, and you can create your book.bib manually
```